---
title: "Software Failure and Reliability Assessment Tool: Report"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#Libraries Needed to genereate report
library(shiny)
library(DT)
library(knitr)
library(gdata)
library(ggplot2)
library(rootSolve)
library(readxl)
```

```{r, include=FALSE}
##Report Specications file
#Contains arguments to key variables that effect the way the report is generated
source('report-specifications.R')
```

```{r, echo=FALSE}
##DATA PREPROCESSING
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/utility/data/Data_Tools.R')

#Input excel file with a single sheet for now
d <- read_excel("~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/model_testing/SYS1_data.xlsx") # TODO: This
cnames <- colnames(d) # Read column names in the input excel file

#Data conversion depending on the type of the input data
tryCatch({
if("FN" %in% cnames && "IF" %in% cnames && "FT" %in% cnames) {
  	FT <- d$FT
  	IF <- d$IF
  	FN <- d$FN
} else if("FN" %in% cnames && "IF" %in% cnames) {
  	FT <- IF_to_FT(d$IF)
  	IF <- d$IF
  	FN <- d$FN
} else if("FN" %in% cnames && "FT" %in% cnames) {
  	IF <- FT_to_IF(d$FT)
  	FT <- d$FT
  	FN <- d$FN
} else if("T" %in% cnames && "FC" %in% cnames && "CFC" %in% cnames) {
  FC <- d$FC
  CFC <- d$CFC
  FT <- FC_to_FT(d$T,d$FC)
  IF <- FT_to_IF(FT)
  FN <- 1:length(FT)
} else if("T" %in% cnames && "FC" %in% cnames) {
  CFC <- FC_to_CFC(d$FC)
  FT <- FC_to_FT(d$T,d$FC)
  IF <- FT_to_IF(FT)
  FN <- 1:length(FT)
} else if("T" %in% cnames && "CFC" %in% cnames) {
  FC <- CFC_to_FC(d$CFC)
  FT <- FC_to_FT(d$T,d$FC)
  IF <- FT_to_IF(FT)
  FN <- 1:length(FT)
} else{
  print("Upload your input data/file formatted according to the SFRAT guidelines")
}
}, error = function(error_condition){
  print("Unable to load in data.")
})
d <- data.frame("FN"=FN,"IF"=IF,"FT"=FT)


#FT
#IF
#FN
#FC
#CFC
```

# Tab 1: Select, Apply, and Analyze Data
Sample of the uploaded input data is shown below: 
```{r, echo=FALSE}
if("T" %in% cnames && "FC" %in% cnames && "CFC" %in% cnames) {
print("Failure counts data")
data_gen.FR <- data.frame("FT"=FT,"IF"=IF,"FN"=FN)
data_gen.FC <- data.frame("FC"=FC, "CFC"=CFC)
data_gen <- list(data_gen.FR,data_gen.FC)
head(data_gen,10)
}else{
  kable(d[1:10,], caption="First ten points of the input data")
}
```

## Cumulative failures
```{r, echo=FALSE}
plot(
  FT, FN, type="s",
  xlab="Cumulative test time", ylab="Cumulative number of failures",
  main = "Cumuative Failures vs. cumulative test time"
)
```

## Times between failures
```{r, echo=FALSE}
plot(
  FT, IF, type="s",
  xlab="Cumulative test time", ylab="Times between successive failures",
  main = "Interfailure times vs. cumulative test time"
)
```

## Failure intensity
```{r, echo=FALSE}
plot(
  FT, 1/IF, type="s",
  xlab="Cumulative test time",ylab="Number of failures per unit time",
  main = "Empirical failure intensity vs. cumulative test time"
)
```

```{r, echo=FALSE}
laplace_trend_test <- function(inter_failure) {
  n <- length(inter_failure)
  failure_time <- IF_to_FT(inter_failure)   
  laplace_trend <- c()
  laplace_trend[1] <- 0
  for(i in 2:n) {
    sumint <- 0
    for(j in 1:(i-1)) {
      sumint <- sumint + failure_time[j]  
    }
    laplace_trend[i] <-(((1/(i-1))*sumint) -(failure_time[i]/2))/(failure_time[i]*(1/(12*(i-1))^(0.5)))
  }
  trend_data <- data.frame(c(1:length(laplace_trend)),laplace_trend)
  names(trend_data) <- c("Index","Laplace_factor")
  return(trend_data)
}

LTT <- laplace_trend_test(IF)

# Two Tailed test
Confidence.lvl <- confidence_lvl # <-- comes from report-specifications.R
Significance <- qnorm(1 - Confidence.lvl)
Z.value.1 <- qnorm(0.1)
Z.value.2 <- qnorm(0.05)
Z.value.3 <- qnorm(0.01)
Z.value.4 <- qnorm(0.001)
Z.value.5 <- qnorm(0.0000001)
Z.value.6 <- qnorm(0.000000001)

#Display significance lines
localTrendPlot <- 
  ggplot(data = LTT, aes(Index, Laplace_factor)) + 
  geom_step() +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) +
  xlab("Failure Number") +
  scale_x_continuous(breaks = round(seq(0 , max(LTT$Index), by = 20), 1)) +
  ylab("Laplace Test Statistic") +
  ggtitle("Laplace Trend Test") + 
  labs(subtitle = bquote("Confidence =" ~.(Confidence.lvl))) +
  geom_hline(yintercept = Significance, color="Red") +
  geom_hline(yintercept = Z.value.1, color="black", linetype = "dotdash", alpha=0.8) +
  geom_hline(yintercept = Z.value.2, color="black", linetype = "dotdash", alpha=0.8) +
  geom_hline(yintercept = Z.value.3, color="black", linetype = "dotdash", alpha=0.8) +
  geom_hline(yintercept = Z.value.4, color="black", linetype = "dotdash", alpha=0.8) +
  geom_hline(yintercept = Z.value.5, color="black", linetype = "dotdash", alpha=0.8) +
  geom_hline(yintercept = Z.value.6, color="black", linetype = "dotdash", alpha=0.8)

localTrendPlot
```

## Running arithmetic average
```{r,echo=FALSE}
running_average_test <- function(inter_failure) {
  n <- length(inter_failure)
  runningAverage <- c()
  for(i in 1:n) {
    sum1 <-0
    for(j in 1:i) {
      sum1 <- sum1 + inter_failure[j]
    }
    runningAverage[i] <- (1/i)*sum1;
  }
  runningAverage <- data.frame(c(1:length(runningAverage)),runningAverage)
  names(runningAverage) <- c("Index","Running_Average")
  return(runningAverage)
}

plot(
  running_average_test(IF), type="s",
  xlab="Failure number", ylab="Running average of interfailure times",
  main="Running arithmetic average test"
)
```

# Tab2: Set Up and Apply Models
```{r, echo=FALSE}
#Add in models to be used
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/DSS/DSS_BM_FT.R')
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/DSS/Model_specifications.R')
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/GO/GO_BM_FT.R')
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/GO/Model_specifications.R')
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/JM/JM_BM.R')
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/JM/Model_specifications.R')
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/GM/GM_BM.R')
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/GM/Model_specifications.R')
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/Wei/Wei_NM_FT.R')
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/models/Wei/Model_specifications.R')
```

## Cumulative failures - JM, GM, GO, DSS, and Weibull
```{r, echo=FALSE}
models <- c() #used for legend
modelList <- list() #passed to plot
modelIterator <- 1;
colors <- c() #for plot line colors
#TODO Fix title

#Apply appropriate models comes from report-specifications.R
  DSS = c()
  if('DSS' %in% models_to_apply && DSS_BM_MLE(FT)!="nonconvergence") { 
    DSS <-  DSS_MVF(DSS_BM_MLE(FT),d)[,2]
    modelList[[modelIterator]] = DSS
    models <- append(models, "DSS")
    colors <- append(colors, DSS_plotcolor)
    modelIterator <- modelIterator + 1
  }

  GO = c()
  if('GO' %in% models_to_apply && GO_BM_MLE(FT)!="nonconvergence") {
    GO <- GO_MVF(GO_BM_MLE(FT),d)[,1]
    modelList[[modelIterator]] = GO
    models <- append(models, "GO")
    colors <- append(colors, GO_plotcolor)
    modelIterator <- modelIterator + 1
  }

  JM = c()
  if('JM' %in% models_to_apply && JM_BM_MLE(IF)!="nonconvergence") { 
    JM <- JM_MVF(JM_BM_MLE(IF),d)[,1]
    modelList[[modelIterator]] = JM
    models <- append(models, "JM")
    colors <- append(colors, JM_plotcolor)
    modelIterator <- modelIterator + 1
  }

  GM = c()
  if('GM' %in% models_to_apply && GM_BM_MLE(IF)!="nonconvergence") { 
    GM <- GM_MVF(GM_BM_MLE(IF),d)[,2]
    modelList[[modelIterator]] = GM
    models <- append(models, "GM")
    colors <- append(colors, GM_plotcolor)
    modelIterator <- modelIterator + 1
  }

  Wei = c()
  if('Wei' %in% models_to_apply && Wei_NM_MLE(FT)!="nonconvergence") { 
    Wei <- Wei_MVF(Wei_NM_MLE(FT),d)[,2]
    modelList[[modelIterator]] = Wei
    models <- append(models, "Wei") 
    colors <- append(colors, Wei_plotcolor)
    modelIterator <- modelIterator + 1
  }

hxy <- data.frame(modelList)
ntrees <- length(models)

plot(FT,FN, type="n",xlab="Cumulative test time", ylab="Cumulative failures")
linetype <- c("p","l","o","b","c","s","S","h")  
lines(FT, FN, type="s")

for (i in 1:ntrees) {
  lines(FT, hxy[,i], type="l", col=colors[i])
}

title("Cumualtive failures vs. cumualtive test time")
legend("bottomright", legend=models, lty=c(1,1), cex=0.8, col=colors)
```


## Times between failures or MTTF
```{r,echo=FALSE}
modelList <- list() #passed to plot
modelIterator <- 1; #used for creating a list
colors <- c() #for plot line colors

#Apply appropriate models comes from report-specifications.R
DSS = c()
if('DSS' %in% models) { 
  DSS <- DSS_MTTF(DSS_BM_MLE(FT),d)[,2]
  modelList[[modelIterator]] = DSS
  colors <- append(colors, DSS_plotcolor)
  modelIterator <- modelIterator + 1
}

GO = c()
if('GO' %in% models) {
  GO <- GO_MTTF(GO_BM_MLE(FT),d)[,2]
  modelList[[modelIterator]] = GO
  colors <- append(colors, GO_plotcolor)
  modelIterator <- modelIterator + 1
}

JM = c()
if('JM' %in% models) { 
  JM <- JM_MTTF(JM_BM_MLE(IF),d)[,2]
  modelList[[modelIterator]] = JM
  colors <- append(colors, JM_plotcolor)
  modelIterator <- modelIterator + 1
}

GM = c()
if('GM' %in% models) { 
  GM <- GM_MTTF(GM_BM_MLE(IF),d)[,2]
  modelList[[modelIterator]] = GM
  colors <- append(colors, GM_plotcolor)
  modelIterator <- modelIterator + 1
}

Wei = c()
if('Wei' %in% models) { 
  Wei <- Wei_MTTF(Wei_NM_MLE(FT),d)[,2]
  modelList[[modelIterator]] = Wei
  colors <- append(colors, Wei_plotcolor)
  modelIterator <- modelIterator + 1
}

hxy <- data.frame(modelList)
ntrees <- length(models)

plot(
  FT, IF, type="n",
  xlab="Cumulative test time", ylab="Times between failures"
)
linetype <- c("p","l","o","b","c","s","S","h")  
lines(FT, IF, type="s")

for (i in 1:ntrees) {
  lines(FT, hxy[,i], type="l", col=colors[i])
}

title("Times between failures vs. cumualtive test time")
legend("topleft", legend=models, lty=c(1,1), cex=0.8, col=colors)
```

## Failure Intensity
```{r, echo=FALSE}
modelList <- list() #passed to plot
modelIterator <- 1;
colors <- c() #for plot line colors

#Apply appropriate models comes from report-specifications.R
DSS = c()
if('DSS' %in% models) { 
  DSS <- DSS_FI(DSS_BM_MLE(FT),d)[,2];
  modelList[[modelIterator]] = DSS
  colors <- append(colors, DSS_plotcolor)
  modelIterator <- modelIterator + 1
}

GO = c()
if('GO' %in% models) {
  GO <- GO_FI(GO_BM_MLE(FT),d)[,2];
  modelList[[modelIterator]] = GO
  colors <- append(colors, GO_plotcolor)
  modelIterator <- modelIterator + 1
}

JM = c()
if('JM' %in% models) { 
  JM <- JM_FI(JM_BM_MLE(IF),d)[,2]; 
  modelList[[modelIterator]] = JM
  colors <- append(colors, JM_plotcolor)
  modelIterator <- modelIterator + 1
}

GM = c()
if('GM' %in% models) { 
  GM <- GM_FI(GM_BM_MLE(IF),d)[,2]; 
  modelList[[modelIterator]] = GM
  colors <- append(colors, GM_plotcolor)
  modelIterator <- modelIterator + 1
}

Wei = c()
if('Wei' %in% models) { 
  Wei <- Wei_FI(Wei_NM_MLE(FT),d)[,2]; 
  modelList[[modelIterator]] = Wei
  colors <- append(colors, Wei_plotcolor)
  modelIterator <- modelIterator + 1
}

hxy <- data.frame(modelList)
ntrees <- length(models)

plot(
  FT, IF, type="n",
  xlab="Cumulative test time", ylab="Failure intensity"
)
linetype <- c("p","l","o","b","c","s","S","h")  
lines(FT, IF, type="s")

for (i in 1:ntrees) {
  lines(FT, hxy[,i], type="l", col=colors[i])
}

title("Cumualtive test time vs. Failure intensity")
legend("bottomright", legend=models, lty=c(1,1), cex=0.8, col=colors)
```

## Reliability Growth
```{r,echo=FALSE}
#Mission time delta value; comes from report-specifications.R
modelList <- list() #passed to plot
modelIterator <- 1;
colors <- c() #for plot line colors

#Apply appropriate models comes from report-specifications.R
DSS = c()
if('DSS' %in% models) { 
  DSS <- DSS_R_growth(DSS_BM_MLE(FT),d, mission_time)[,2]
  modelList[[modelIterator]] = DSS
  colors <- append(colors, DSS_plotcolor)
  modelIterator <- modelIterator + 1
}

GO = c()
if('GO' %in% models) {
  GO <- GO_R_growth(GO_BM_MLE(FT),d,mission_time)[,2]
  modelList[[modelIterator]] = GO
  colors <- append(colors, GO_plotcolor)
  modelIterator <- modelIterator + 1
}

JM = c()
if('JM' %in% models) { 
  JM <- JM_R_growth(JM_BM_MLE(FT),d,mission_time)[,2]
  modelList[[modelIterator]] = JM
  colors <- append(colors, JM_plotcolor)
  modelIterator <- modelIterator + 1
}

GM = c()
if('GM' %in% models) {
  GM <- GM_R_growth(GM_BM_MLE(FT),d,mission_time)[,2]
  modelList[[modelIterator]] = GM
  colors <- append(colors, GM_plotcolor)
  modelIterator <- modelIterator + 1
}

Wei = c()
if('Wei' %in% models) { 
  Wei <- Wei_R_growth(Wei_NM_MLE(FT),d,mission_time)[,2]
  modelList[[modelIterator]] = Wei
  colors <- append(colors, Wei_plotcolor)
  modelIterator <- modelIterator + 1
}

hxy <- data.frame(modelList)
ntrees <- length(hxy)

plot(
  FT, 
  seq(from=0, to=max(hxy), by=max(hxy)/(length(FT)-1)),
  type="n",
  xlab="Cumulative test time", ylab="Reliability growth"
)

linetype <- c("p","l","o","b","c","s","S","h")  

for (i in 1:ntrees) { 
  lines(FT, hxy[,i], type="l", col=colors[i]) ##Limit the upperbound to maximum value
} 

title("Reliability growth vs. cumualtive test time")
legend("topleft", legend=models, lty=c(1,1), cex=0.8, col=colors)
```

# Tab3: Query Model Results
```{r,echo=FALSE}
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/utility/prediction/Detailed_prediction.R')

#Setting Up The Table
predTable <- matrix(NA, nrow = 5, ncol = 3)
rownames(predTable) <- c("DSS","GO","JM","GM","Wei")
colnames(predTable) <- c("Time to achieve specified reliability","Expected number of failures","Expected time to N failure")

##Calulating Future Failures
#Time to achieve specified reliability
predTable[,1] <- c(
  get_reliability_t("DSS",DSS_BM_MLE(FT),desired_reliability,reliability_interval_length,last(FT),num_failures_to_predict),
  get_reliability_t("GO",GO_BM_MLE(FT),desired_reliability,reliability_interval_length,last(FT),num_failures_to_predict),
  get_reliability_t("JM",JM_BM_MLE(IF),desired_reliability,reliability_interval_length,last(IF),num_failures_to_predict),
  get_reliability_t("GM",GM_BM_MLE(IF),desired_reliability,reliability_interval_length,last(IF),num_failures_to_predict),
  get_reliability_t("Wei",Wei_NM_MLE(FT),desired_reliability,reliability_interval_length,last(FT),num_failures_to_predict)
)
#Expected number of failures
predTable[,2] <- c(
  get_prediction_k("DSS",DSS_BM_MLE(FT),additional_time_software_will_run,last(FT),length(FT)),
  get_prediction_k("GO",GO_BM_MLE(FT),10,last(FT),length(FT)),
  get_prediction_k("JM",JM_BM_MLE(IF),10,last(FT),length(FT)),
  get_prediction_k("GM",GM_BM_MLE(IF),10,last(FT),length(FT)),
  get_prediction_k("Wei",Wei_NM_MLE(FT),10,last(FT),length(FT))
)
#Expected time to N failure
predTable[,3] <- c(
  get_prediction_t("DSS",DSS_BM_MLE(FT),1,last(FT),length(FT)),
  get_prediction_t("GO",GO_BM_MLE(FT),1,last(FT),length(FT)),
  get_prediction_t("JM",JM_BM_MLE(IF),1,last(FT),length(FT)),
  get_prediction_t("GM",GM_BM_MLE(IF),1,last(FT),length(FT)),
  get_prediction_t("Wei",Wei_NM_MLE(FT),1,last(FT),length(FT))
)

#As of right now, the table can only hold a single value
#TODO:multiple rows for each falure prediction

kable(predTable)
```

# Tab4: Evaluate Models
```{r,echo=FALSE}
source('~/Dropbox/NASA OSMA SARP/Script/srt-3.core-master/utility/metrics/GOF.R')
#Setup Table
GOFTable <- matrix(NA, nrow = 5, ncol = 2)
rownames(GOFTable) <- c("DSS", "GO", "JM", "GM", "Wei")
colnames(GOFTable) <- c("AIC", "PSSE")

#Calculate AIC
GOFTable[,1] <- c(
  aic(2, DSS_lnL(FT, DSS_BM_MLE(FT))),
  aic(2, GO_lnL(FT, GO_BM_MLE(FT))),
  aic(2, JM_lnL(IF, JM_BM_MLE(IF))),
  aic(2, GM_lnL(IF, GM_BM_MLE(IF))),
  aic(3, Wei_lnL(FT, Wei_NM_MLE(FT)))
)

#Calculate PSSE
GOFTable[,2] <- c(
  psse("DSS", FT, DSS_BM_MLE(FT), percent_data_for_PSEE),
  psse("GO", FT, GO_BM_MLE(FT), percent_data_for_PSEE),
  psse("JM", FT, JM_BM_MLE(IF), percent_data_for_PSEE),
  psse("GM", FT, GM_BM_MLE(IF), percent_data_for_PSEE),
  psse("Wei", FT, Wei_NM_MLE(FT), percent_data_for_PSEE)
)

kable(GOFTable)
```
